\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-10 paper/paper.tex
1 kleine verandering

\subsection{Testing}
In the experiment, two cases were tested: a basic case, without preprocessing, and a case with preprocessing. In both cases a timer was added to the code. The timer started before any other piece of code and ended after the algorithms were completely finished. This way all the required computation is timed, including the loading of the graph, the additional time used to run preprocessing algorithms and the finding of isomorphisms.

>>>>

\subsection{Testing}
In the experiment, two cases were tested: a basic case, without preprocessing, and a case with preprocessing. In both cases a timer was added to the code. The timer started before any other piece of code and ended after the algorithms were completely finished. This way all the required computations are timed, including the loading of the graph, the additional time used to run preprocessing algorithms and the finding of isomorphisms.
